\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-05-19 doc/USER_MANUAL/manual_SPECFEM3D.tex
added a description about OpenMP

@@

>>>>

\section{Adding OpenMP support in addition to MPI}

OpenMP support can be enabled in addition to MPI. However, in many cases performance will not improve
because our pure MPI implementation is already heavily optimized and thus the resulting code will in fact       
be slightly slower. A possible exception could be IBM BlueGene-type architectures.

To enable OpenMP, uncomment the OpenMP compiler option in two lines in file \texttt{src/specfem3D/Makefile.in}
(before running \texttt{configure}) and also uncomment the \texttt{\#define USE\_OPENMP} statement in file\\
\texttt{src/specfem3D/specfem3D.F90}.

The DO-loop using OpenMP threads has a SCHEDULE property. The OMP\_SCHEDULE
environment variable can set the scheduling policy of that DO-loop.
Tests performed by Marcin Zielinski at SARA (The Netherlands) showed that often
the best scheduling policy is DYNAMIC with the size of the chunk equal to the number of
OpenMP threads, but most preferably being twice as the number of
OpenMP threads (thus chunk size = 8 for 4 OpenMP threads etc).
If OMP\_SCHEDULE is not set or is empty, the DO-loop will assume generic
scheduling policy, which will slow down the job quite a bit.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
